Gammapy: A Python package for gamma-ray astronomy

### 2023-06-12 src/ms-review.tex

Where the expected number of events in a \gammaray observation is given by:
 \begin{equation}
	 \begin{split}
		N_{\mathrm{Pred}}(p, E; \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \circledast \left[ PSF \circledast \left( A_{\rm eff} \cdot t_{\rm obs} \cdot \Phi(\hat{\theta}) \right) \right]\\
						& + Bkg(p, E) \cdot t_{\rm obs}
	 \end{split}
 \end{equation}

With the IRF components described in the previous section as well as an analytical model to describe the
intensity of the radiation from gamma-ray sources as a function of the energy, $E_{\rm true}$,
and of the position in the FoV, $p_{\rm true}$:
%
\begin{equation}
    \Phi(p_{\rm true}, E_{\rm true}; \hat{\theta}), [\Phi] = \si{TeV^{-1}.cm^{-2}.s^{-1}}
    \label{eq:general_source_model}
\end{equation}
Where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. 
Observations can be either modeled individually, or in a joint likelihood analysis.
In the latter case the total (joint) log-likelihood is given by the sum of the log-likelihoods
per observation $\mathcal{L} = \sum{i=0}^M \mathcal{C_i}$ for M observations. Other fit
statistics such as \textit{WStat} or a simple $\chi^2$ for flux points are also often used
and are supported by \gammapy as well. Models can be simple analytical models or more complex
ones from radiation mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{0}$ decay).

>>>>

Where the expected number of events for the observation is given by forward folding a source model through
the instrument response:
 \begin{equation}
	 \begin{split}
		N_{\mathrm{Pred}}(p, E; \hat{\theta})\ {\rm d}p\ {\rm d}E =  &E_{\rm disp} \circledast \left[ PSF \circledast \left( A_{\rm eff} \cdot t_{\rm obs} \cdot \Phi(\hat{\theta}) \right) \right]\\
						& + Bkg(p, E) \cdot t_{\rm obs}
	 \end{split}
 \end{equation}

The equation includes the IRF components described in the previous section, as well as an analytical model to describe the
intensity of the radiation from \gammaray sources as a function of the energy, $E_{\rm true}$,
and of the position in the FoV, $p_{\rm true}$:
%
\begin{equation}
    \Phi(p_{\rm true}, E_{\rm true}; \hat{\theta}), [\Phi] = \si{TeV^{-1}.cm^{-2}.s^{-1}}
    \label{eq:general_source_model}
\end{equation}

Where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. 
Observations can be either modeled individually, or in a joint likelihood analysis.
In the latter case the total (joint) log-likelihood is given by the sum of the log-likelihoods
per observation $\mathcal{L} = \sum{i=0}^M \mathcal{C_i}$ for M observations. Other fit
statistics such as \textit{WStat}, where the background is estimated from an independent
measurement or a simple $\chi^2$ for flux points are also often used
and are supported by \gammapy as well. Models can be simple analytical models or more complex
ones from radiation mechanisms of accelerated particle populations (e.g. inverse Compton or $\pi^{0}$ decay).
